### 2020-06-28 thesis_template/3_Body/model/knn.tex
presentation
corrected

Finally, we examine performance of a Machine Learning (ML) algorithms. 
The goal of this experiment is to evaluate better memory management strategies in ML algorithms developed with Rust.
We employ K-Nearest-Neighbors (KNN) for ML algorithm to be studied in our experiments.
Our KNN algorithms perform document classification on Wikipedia page data set described in Section~\ref{sec:eval_setdetail}.

The algorithms have 4 phase; load, preprocess, query, and combine phase. 
Before these phase, we separate data sets into 8 partitions to run these in different threads. 
The algorithms spawn threads at the beginning ,and in the load phase partition of files are loaded in each threads. 
In preprocessing phase, the algorithm process document strings to generate Term-frequencies (Tfs) matrices and other data structures. 
In query phase, it calculates cosine similarities between all combination of train and test observations and select to top \(K\) nearest neighbors. 
In combine phase, the results from each batch and from each are combined. 
Based on our experiments result, the runtime in preprocess and query phase are significantly larger than other two phases.
Therefore, we focus discussion in these two phases considering them bottlenecks in our KNN algorithms.

@@

Method parameter is specified to select memory management strategy used in preprocess phase. 
In preprocess phase, the algorithm generates many intermediate data structures using same String elements.
Deep-copy method deeply copies String to generate intermediate data structures. Arc method use Atomic Reference Count (Arc) to wrap String elements in the original data structure and 
clone Arc when the elements are used in other data structures. As Experiment 4 had shown in in Section~\ref{sec:eval_treeagg}, deep-copy of complex objects is more expensive than cloning Arc. 
String is a sort of objects allocated in heap and copied many times in preprocess phase. Therefore, it is worth to assess which method can be better memory management strategy in our experiments.

Strategy parameter controls memory management strategy used in both preprocess and query phase.
Strategy 1 keeps all intermediate data structures and numeric matrix objects from preprocess to query phase. 
Strategy 2 removes these data structures and objects as soon as they are not needed. 
These strategies differ from each other in terms of memory usage and frequency of memory deallocations.
These may cause significant runtime difference of the algorithms.

Number of batch controls number and size of batch for each partition. This parameter varies size of intermediate data structures and numeric matrices, and 
frequency of memory deallocations. 
The size of each batch is defined in 6250 pages when we have 2 batches, and 4166 or 4167 when we have 3 batches. 
The parameter k specifies number of dimension of feature matrices created out of preprocess phase. 
By controlling this, it determines size of intermediate data structures and numeric matrices.

@@

\subsection{Result}
\label{sec:history}
Figure~\ref{fig:total}, ~\ref{fig:preprocess}, and ~\ref{fig:query} show the runtime performance of our KNN algorithms in total, preprocess, and query phase respectively. 
The algorithms used in our experiments are indexed in Table~\ref{tab:algorithm}. We call each algorithm in algorithm number for easy understanding.
The Algorithm 3 with 20K and 25K dimension, and the Algorithm 1 with 25K dimension whose runtime is showing 0 seconds are algorithms that are terminated during execution due to fail of memory allocation.

Figure~\ref{fig:total} shows Algorithm 8 shows much slower performance compare to the other algorithms.
Algorithm 7 also starts to slow down as we increase the number of dimension.

As shown in Figure~\ref{fig:preprocess}, the algorithms using Arc is much slower than using deep-copy in preprocessing phase. 
Algorithm 6 is 38\%  slower than Algorithm 6 in dimension of 25K. 
In addition, the algorithms with strategy 2 are slower than with strategy 1. 
For example, Algorithm 6 is about 85\% slower than one Algorithm 2 in dimension of 25K.
The algorithms with 3 batches are slower that ones with 2 batches. Furthermore, as we increase the number of dimension, the number of batch becomes more and more critical to runtime performance of the algorithms with deep-copy.
The runtime ratios of difference from Algorithm 7 to Algorithm 8 are about 44\%, 28\%, and 39\% for dimension of 15K, 20K, and 25K respectively. 
However, those from Algorithm 5 to Algorithm 6 are about 11\%, 28\%, and 54\%. The ratios of difference increase proportionally to the number of dimension.

@@

\subsection{Discussion}
\label{sec:history}
In preprocess phase, the algorithms using Arc method performs worse than ones with deep-copy method. 
This result may seem to contradict to the result of Experiment 4 in Section~\ref{sec:eval_treeagg}.
In Experiment 4, complex objects, CustomerOwned, are cloned with Arc or deep-copied. 
In this Experiment 5, we however get Arc or deep-copy of String instead of complex object.
The result explains deep-copying String is much inexpensive than deep-copying the complex object and 
using deep-copy method is actually efficient than using Arc to share String. 
Therefore, we need to make decision which method to use depending on size and complexity of objects.

In addition, use of different strategies in preprocess phase explains how deallocations of intermediate data structures and drops of their variables impact algorithm's runtime performance.
The result shows deallocations of intermediate data costs a lot; Algorithm 6 is 85\% slower than Algorithm 2.
This may be more severe bottleneck for algorithms using Arc; Algorithm 8 is 102\% slower than Algorithm 4.
This is the same reason explained in Experiment 4. 
Arc has to check reference count and its atomic operation is expensive.

The impact of batch number can explain how frequency of memory de/allocation affects runtime performance. 
Dealing with more number of batch has negative impacts on runtime performance because it triggers more frequent memory de/allocation.
In addition, as we increase the number of dimension, the ration of runtime difference among different numbers of batch for the algorithms with deep-copy, but not for ones with Arc.
This is because algorithm with Arc does not de/allocate memory as much frequent as ones with deep-copy.
The intermediate data structures mealy get reference to String values without actually allocating memory for copied Strings.

@@

However, we can see significant degradation in Algorithm 7 with 20K and 25K dimension and Algorithm 8 with 15K, 20K, and 25K dimension. 
By using strategy 2, we deallocate the numeric matrices and vectors in query phase. However, it is difficult to think that these contiguous memory deallocations cause the degradation. 
If that is so, Algorithm 5 and 6 should also show some overheads. No page-swapping does not happen during the execution. 
One possible reason is that these algorithms suffer from the allocation of numeric matrices and vectors due to previous deallocation of intermediate data structures in preprocess phase. 
The frequent deallocations and low locality of Arc may lead long free-space-list making difficult to search enough spaces to allocate numeric matrices and vectors.
The other possibility is that the frequent deallocations and low locality of Arc cause cache of numeric matrices and vectors. 
The computation on these numeric objects may slow down due to their caching levels. 
To conclude these discussion, we need to conduct more experiments and deeper analysis. 
However, we push those discussion in next paper.

In a part of conclusion, using Arc to String may be overhead. Considered the result from Experiment 4, we need careful consideration which object to use which strategy, deep-copy and Arc.
In addition, frequent memory deallocation can lead to slower runtime performance. 
Therefore, we need to decide when to deallocate unused values taking account of memory capacity.

>>>>

Finally, we examine the performance of Machine Learning (ML) algorithms. 
The goal of this experiment is to evaluate better memory management strategies in ML algorithms developed with Rust.
We employ K-Nearest-Neighbors (KNN) for ML algorithms to be studied in our experiments.
Our KNN algorithms perform document classification on Wikipedia page data set described in Section~\ref{sec:eval_setdetail}.

The algorithms have 4 phases; load, preprocess, query, and combine phase. 
Before these phases, we separate data sets into 8 partitions to run these in different threads. 
The algorithms spawn threads at the beginning, and in the load phase partition of files are loaded in each threads. 
In the preprocessing phase, the algorithm process document strings to generate Term-frequencies (Tfs) matrices and other data structures. 
In the query phase, it calculates cosine similarities between all combination of train and test observations and select to top \(K\) nearest neighbors. 
In combine the phase, the results from each batch and from each thread are combined. 
Based on our experiment's result, the runtime in preprocess and query phase are significantly larger than other two phases.
Therefore, we focus our discussion in these two phases considering them bottlenecks in our KNN algorithms.

@@

Method parameters are specified to select memory management strategy used in preprocess phase. 
In preprocess the phase, the algorithm generates many intermediate data structures using same String elements.
Deep-copy method deeply copies String to generate intermediate data structures. Arc method use Atomic Reference Count (Arc) to wrap String elements in the original data structure and 
clone Arc when the elements are used in other data structures. As Experiment 4 had shown in in Section~\ref{sec:eval_treeagg}, deep-copy of complex objects is more expensive than cloning Arc. 
String is a sort of object allocated in heap and copied many times in preprocess phase. Therefore, it is worth assessing which method can be a better memory management strategy in our experiments.

Strategy parameter control memory management strategy used in both preprocess and query phase.
Strategy 1 keeps all intermediate data structures and numeric matrix objects from preprocess to query phase. 
Strategy 2 removes these data structures and objects as soon as they are not needed. 
These strategies differ from each other in terms of memory usage and frequency of memory deallocations.
These may cause significant runtime difference of the algorithms.

Number of batch controls number and size of batch for each partition. This parameter varies size of intermediate data structures and numeric matrices, and 
frequency of memory deallocations. 
The size of each batch is defined in 6,250 pages when we have 2 batches, and 4166 or 4167 when we have 3 batches. 
The parameter k specifies the number of dimensions of feature matrices created out of the preprocess phase. 
By controlling this, it determines size of intermediate data structures and numeric matrices.

@@

\subsection{Result}
\label{sec:history}
Figures~\ref{fig:total}, ~\ref{fig:preprocess}, and ~\ref{fig:query} show the runtime performance of our KNN algorithms in total, preprocess, and query phase respectively. 
The algorithms used in our experiments are indexed in Table~\ref{tab:algorithm}. We call each algorithm in algorithm number for easy understanding.
The Algorithm 3 with 20K and 25K dimension, and the Algorithm 1 with 25K dimension whose runtime is showing 0 seconds are algorithms that are terminated during execution due to fail of memory allocation.

Figure~\ref{fig:total} shows Algorithm 8 shows much slower performance compare to the other algorithms.
Algorithm 7 also starts to slow down as we increase the number of dimensions.

As shown in Figure~\ref{fig:preprocess}, the algorithms using Arc is much slower than using deep-copy in preprocessing phase. 
Algorithm 8 is 38\%  slower than Algorithm 6 in dimension of 25K. 
In addition, the algorithms with strategy 2 are slower than with strategy 1. 
For example, Algorithm 6 is about 85\% slower than one Algorithm 2 in dimension of 25K.
The algorithms with 3 batches are slower that ones with 2 batches. Furthermore, as we increase the numbers of dimension, the number of batches becomes more and more critical to runtime performance of the algorithms with deep-copy.
The runtime ratios of difference from Algorithm 7 to Algorithm 8 are about 44\%, 28\%, and 39\% for dimension of 15K, 20K, and 25K respectively. 
However, those from Algorithm 5 to Algorithm 6 are about 11\%, 28\%, and 54\%. The ratios of difference increase proportionally to the number of dimensions.

@@

\subsection{Discussion}
\label{sec:history}
In the preprocess phase, the algorithms using Arc method perform worse than ones with deep-copy method. 
This result may seem to contradict to the result of Experiment 4 in Section~\ref{sec:eval_treeagg}.
In Experiment 4, complex objects, CustomerOwned, are cloned with Arc or deep-copied. 
In this Experiment 5, we however get Arc or deep-copy of String instead of complex object.
The result explains deep-copying String is more inexpensive than deep-copying the complex object and 
using deep-copy method is actually more efficient than using Arc to share String. 
Therefore, we need to make decision which method to use depending on size and complexity of objects.

In addition, the use of different strategies in the preprocess phase explains how deallocations of intermediate data structures and drops of their variables impact algorithm's runtime performance.
The result shows deallocations of intermediate data costs a lot; Algorithm 6 is 85\% slower than Algorithm 2.
This may be a more severe bottleneck for algorithms using Arc; Algorithm 8 is 102\% slower than Algorithm 4.
This is the same reason explained in Experiment 4. 
Arc has to check reference count and its atomic operation is expensive.

The impact of batch number can explain how frequency of memory de/allocation affects runtime performance. 
Dealing with more number of batch has negative impacts on runtime performance because it triggers more frequent memory de/allocation.
In addition, as we increase the number of dimension, the ration of runtime difference among different numbers of batch for the algorithms with deep-copy, but not for ones with Arc.
This is because algorithm with Arc does not de/allocate memory as much frequently as ones with deep-copy.
The intermediate data structures merely get reference to String values without actually allocating memory for copied Strings.

@@

However, we can see significant degradation in Algorithm 7 with 20K and 25K dimensions and Algorithm 8 with 15K, 20K, and 25K dimensions. 
By using strategy 2, we deallocate the numeric matrices and vectors in query phase. However, it is difficult to think that these contiguous memory deallocations cause the degradation. 
If that is so, Algorithm 5 and 6 should also show some overheads. No page-swapping happens during the execution. 
One possible reason is that these algorithms suffer from the allocation of numeric matrices and vectors due to previous deallocation of intermediate data structures in preprocess phase. 
The frequent deallocations and low locality of Arc may lead long free-space-list making difficult to search enough spaces to allocate numeric matrices and vectors.
The other possibility is that the frequent deallocations and low locality of Arc cause cache of numeric matrices and vectors. 
The computation on these numeric objects may slow down due to their caching levels. 
To conclude this discussion, we need to conduct more experiments and deeper analysis. 
However, we push those discussion to next paper.

As a part of the conclusion, using Arc to String may be overhead. Considering the result from Experiment 4, we need careful consideration which object to use which strategy, deep-copy and Arc.
In addition, frequent memory deallocation can lead to slower runtime performance. 
Therefore, we need to decide when to deallocate unused values taking account of memory capacity.

### 2020-06-28 thesis_template/3_Body/model/merge_sort_experiment.tex
done
corrected

Sorting algorithm like merge-sort is a very ubiquitous algorithm in any computation. 
Especially in Big Data processing, merge-sort algorithm de/allocates contiguous memory for partitions of sorted vector multiple times.
We are interested in memory de/allocation pattern in merge-sort algorithm, because it generates many intermediate data structures and delete them many times.

As explained in Experiment 2 in Section~\ref{sec:eval_refcount}, deletion of Rc has significant overhead than normal reference. 
By learning this result, our assumption here is that deletion of Arc has also overhead when we compare to normal reference. 
In many situation where developer writes a multithreading code, Arc is used and the deletion happens multiple times. 
To assess runtime overhead of algorithm with Arc, We implement merge-sort algorithm in two different ways. 
One is sharing source vector with Arc. The other is passing reference of source vector to child thread.

@@

The splitting phase is merely acquiring index of range. At this phase, multiple threads are generated and Arc or reference of source vector are passed by calling recursive function. 
Copying phase occurs in the base case of the recursive call. The element in the source vector in a certain index is deep-copied into newly allocated vector.
At merge phase, merge function receives two sorted independent vector and merge them into single new vector.

We use scope method from crossbeam crate to perform multithread programming. 
Scoped thread can have reference to value from its parent thread by ensuring children threads are joined before their parent thread returns value. 
By using scoped thread, we can implement two merge-sort algorithms in identical way except whether the function receives Arc or reference of source vector.
The representations of source vector for each algorithm are shown in Figure~\ref{fig:source_merge_sort}.
The elements of source vector are CustomerOwned objects. We generates source vectors in size of 4, 8, 12 and 16 million.
Finally, merge-sort is performed based on value of key field. The figure shows the result for runtime performance of merge-sort algorithms on difference size of vectors.

@@

\subsection{Result}
Figure~\ref{fig:source_merge_sort} shows the runtime performance of our merge-sort algorithm with specified Vec sizes. 
The blue and yellow bar charts represent the runtime performance of merge-sort algorithm using reference and Arc respectively. 
The result says that algorithms with Arc is about 21\% slower than algorithms with reference.

@@

\subsection{Discussion}
The reason why merge-sort algorithm with Arc is much slower than one with reference is 
the same for the reason why dropping Rc shows overhead compared to dropping reference.
Arc has to check the number of variable pointing to the actual content and decide 
deallocate the memory or not.

In addition, Arc uses atomic operations for tis reference counting. Atomic operations bring thread-safety, but they are more expensive than ordinary memory accesses.
Therefore, when sharing reference counting between threads is not required, using Rc is the recommended way \cite{RustArcPage}.

In the situation like our experiment, normal reference can be used instead of Arc to share data between threads. 
This solution results in better runtime performance in our experiment. Therefore, one should use reference to share data among different threads 
whenever it is possible.

>>>>

Sorting algorithm like merge-sort is a very ubiquitous algorithm in any computation. 
Especially in Big Data processing, merge-sort algorithms de/allocate contiguous memory for partitions of sorted vector multiple times.
We are interested in memory de/allocation patterns in merge-sort algorithm, because it generates many intermediate data structures and deletes them many times.

As explained in Experiment 2 in Section~\ref{sec:eval_refcount}, deletion of Rc has significant overhead than normal reference. 
By learning this result, our assumption here is that deletion of Arc also has overhead when we compare to normal reference. 
In many situations where a developer writes a multithreading code, Arc is used and the deletion happens multiple times. 
To assess runtime overhead of algorithms with Arc, we implement merge-sort algorithm in two different ways. 
One is sharing source vector with Arc. The other is passing reference of source vector to child thread.

@@

The splitting phase is merely acquiring index of range. At this phase, multiple threads are generated and Arc or reference of source vector are passed by calling recursive function. 
Copying phase occurs in the base case of the recursive call. The element in the source vector in a certain index is deep-copied into newly allocated vector.
At merge phase, merge function receives two sorted independent vectors and merges them into a single new vector.

We use scope method from crossbeam crate to perform multithread programming. 
Scoped thread can have reference to value from its parent thread by ensuring children threads are joined before their parent thread returns value. 
By using scoped thread, we can implement two merge-sort algorithms in an identical way except whether the function receives Arc or reference of source vector.
The representations of source vectors for each algorithm are shown in Figure~\ref{fig:source_merge_sort}.
The elements of source vector are CustomerOwned objects. We generate source vectors in sizes 4, 8, 12 and 16 million.
Finally, merge-sort is performed based on value of key field. The figure shows the result for runtime performance of merge-sort algorithms on difference sizes of vectors.

@@

\subsection{Result}
Figure~\ref{fig:source_merge_sort} shows the runtime performance of our merge-sort algorithm with specified Vec sizes. 
The blue and yellow bar charts represent the runtime performance of merge-sort algorithm using reference and Arc respectively. 
The result says that algorithms with Arc is about 21\% slower than algorithms with reference.
The memory usage for algorithms with 16 million Customer objects are about 26G bytes.

@@

\subsection{Discussion}
The reason why merge-sort algorithms with Arc is much slower than one with reference is 
the same for the reason why dropping Rc shows overhead compared to dropping reference.
Arc has to check the number of variable pointing to the actual content and decide 
deallocate the memory or not.

In addition, Arc uses atomic operations for reference counting. Atomic operations bring thread-safety, but they are more expensive than ordinary memory accesses.
Therefore, when sharing reference counting between threads is not required, using Rc is the recommended way \cite{RustArcPage}.

In situations like our experiment, normal reference can be used instead of Arc to share data between threads. 
This solution results in better runtime performance in our experiment. Therefore, one should use reference to share data among different threads 
whenever it is possible.

### 2020-06-28 thesis_template/3_Body/model/tree_aggregate_experiment.tex
corrected

In our experiment, tree-aggregation algorithms are examined in multi-threading. This experiment is to evaluate the impact of having Arc (Atomic Reference Counting) as elements of vector. 
In Big Data mining tool, such as Spark, it generates intermediate objects from original source vector. In tree-aggregation, aggregated HashMap like data structure is created in each step or node. 
Acquisition of elements in source vector is required to perform this aggregation. There are several ways.

One way is deep-copy elements of vector. This solution allocated newly created objects by deep-copy. 
Aggregation is performed on copied objects, stores them in the data structure and sends it to next node. 
Deep-copy generates duplicates of objects in vector and aggregated data structure. 
This can lead to memory intensive moment when we need memory space for the duplicated objects in addition.

The other way is to get reference to the elements. Since an original source vector is deallocated after a local aggregation,
Simple reference to elements does not live long enough and allow the aggregation result to be sent to next node. 
Instead of simple borrowing, we need owner in the aggregation result. Reference Counting (Rc) in Rust is a way to have multiple owners to a value. 
Since our experiment is implemented in multithreading, Atomic Reference Counting (Arc) is used instead of Rc. With Arc, multiple ownership pointer can be 
possessed by different variables across multiple threads. Therefore a value is not deallocated until all of owners to it are dropped. 
This does not require extra memory allocation, because only acquisition of new ownership to value is needed. 
However, as explained in the last section deletion of Arc type checks whether the value is still owned by other variables. 
This checking may be an overhead in algorithms where generate a lot of intermediate data structures, because deletion of the data structures occurs in frequent.

Two algorithms are implemented using the above two different methods and evaluated their runtime performance. 
We perform aggregation to CustomerOwned based on last\_name field. 
Before tree-aggregation algorithms are run, partitions of Vec$<$CustomerOwned$>$ or of Vec$<$Arc$<$CustomerOwned$>>$ are created ,serialized, and stored in disk.
A tree-aggregate algorithm has main three phases: loading, aggregating, and combining phase. 
At loading phase the algorithm generate threads. In each node, it loads serialized CustomerOwned partition from disk and deserialize them.
At aggregating phase, aggregation is performed on each partition by last\_name field. Once a node finishes aggregation, it sends result to parent node. 
After parent nodes receive aggregation results from all of its children nodes, it joins all aggregation results including its and sends next parent. 
This joining aggregation results is considered as combining phase.

Two kinds of algorithm are implemented. One algorithm performs aggregation by deep-copying elements from source vector loaded from disk. 
In the other algorithm, each element of source vector is wrapped in Arc, and its reference is acquired while aggregation. 
The difference of the both algorithm codes are represented in Figure~\ref{fig:arc_tree} and in Figure~\ref{fig:deep_tree}.
If we glance the codes, the notable difference is only when we acquire an element from CustomerOwned Vec to construct an aggregated data structure.
Therefore, there is few difference between two kinds of tree-aggregate algorithm in terms of code appearance.

@@

\subsection{Result}
Figure~\ref{fig:ex_tree_agg} shows runtime performance of two tree-aggregate algorithms. 
The runtime of algorithm with deep-copy is about 40 to 50\% slower than algorithm with Arc for every vector size.

@@

At the aggregating phase, each object is deep-copied or acquired with Arc once during the runtime in order to construct aggregated data structures.
If total number of object is 1 million, the all of 1 million objets are deep-copied or cloned with Arc once during execution. 
Deep-copy allocates new memory for copied object. On the other hand, clone with Arc is merely acquisition of additional owner. 
Therefore, deep-copy is more expensive in terms of runtime and also use of memory than clone with Arc. 
Deep-copy processes all the original objects to generate newly deep-copied objects. 
This process has overhead and the existence of both original and copied objects doubles its memory usage.

After construction of aggregated data structure, the dropping variables of original object occurs at the end of aggregating phase.
In the algorithm with deep-copy, these variables are owners so that drop of variables triggers deallocation of actual values.
In the algorithm with Arc, the variables are Arc. The aggregated data structure contains Arc pointing to the same values pointed by original Arc.
Since the aggregated data structure continue to live after aggregating phase, drop of original Arcs does not triggers deallocation of values. 
Therefore, drop of original variables can shows overhead of memory deallocation in algorithm with deep-copy, 
and overhead of checking reference count of Arc in algorithm with Arc.

In addition, memory access from Arc is slower than ordinal variable due to the atomic operations. This may be potential overhead of the algorithm with Arc.

Considered these theoretical analysis and result of our experiment, using Arc improves runtime performance and memory usage compared to algorithm using deep-copy in tree-aggregate algorithm.

>>>>

In our experiment, tree-aggregation algorithms are examined in multi-threading. This experiment is to evaluate the impact of having Arc (Atomic Reference Counting) as elements of vectors. 
In Big Data mining tools, such as Spark, it generates intermediate objects from the original source vector. In tree-aggregation, aggregated HashMap like data structures is created in each step or node. 
Acquisition of elements in the source vector is required to perform this aggregation. There are several ways.

One way is to deep-copy elements of the vector. This solution allocates newly created objects by deep-copy. 
Aggregation is performed on copied objects, they are stored in the data structure and sent to next node. 
Deep-copying generates duplicates of objects in vectors and aggregated data structure. 
This can lead to memory intensive moments when we need memory space for the additional duplicated objects.

The other way is to get reference to the elements. Since an original source vector is deallocated after a local aggregation,
simple references to elements do not live long enough and allow the aggregation result to be sent to next node. 
Instead of simple borrowing, we need owners in the aggregation result. Reference Counting (Rc) in Rust is a way to have multiple owners to a value. 
Since our experiment is implemented in multithreading, Arc (Arc) is used instead of Rc. With Arc, multiple ownership pointers can be 
possessed by different variables across multiple threads. Therefore, a value is not deallocated until all owners to it are dropped. 
This does not require extra memory allocation, because only acquisition of new ownership to the value is needed. 
However, as explained in the last section deletion of Arc type checks whether the value is still owned by other variables. 
This checking may be an overhead in algorithms that generate a lot of intermediate data structures, because deletion of the data structures occurs frequently.

Two algorithms are implemented using the above two methods and their runtime performance is evaluated . 
We perform aggregation to CustomerOwned based on last\_name field. 
Before tree-aggregation algorithms are run, partitions of Vec$<$CustomerOwned$>$ or of Vec$<$Arc$<$CustomerOwned$>>$ are created, serialized, and stored in disk.
A tree-aggregate algorithm has main three phases: loading, aggregating, and combining phase. 
At loading phase the algorithm generates threads. In each node, it loads serialized CustomerOwned partition from disk and deserialize them.
At aggregating phase, aggregation is performed on each partition by last\_name field. Once a node finishes aggregation, it sends result to parent node. 
After parent nodes receive aggregation results from all of its children nodes, it joins all aggregation results including its and sends to the next parent. 
This joining aggregation results is considered as combining phase.

Two kinds of algorithms are implemented. One algorithm performs aggregation by deep-copying elements from a source vector loaded from a disk. 
In the other algorithm, each element of the source vector is wrapped in Arc, and its reference is acquired while aggregation. 
The difference between the both algorithm codes are represented in Figure~\ref{fig:arc_tree} and in Figure~\ref{fig:deep_tree}.
If we glance at the codes, the notable difference is only when we acquire an element from CustomerOwned Vec to construct an aggregated data structure.
Therefore, there are few difference between the two kinds of tree-aggregate algorithm in terms of code appearance.

@@

\subsection{Result}
Figure~\ref{fig:ex_tree_agg} shows runtime performance of two tree-aggregate algorithms. 
The runtime of algorithm with deep-copy is about 40 to 50\% slower than algorithm with Arc for every vector size. 
The memory usage of algorithm with Arc and size of 8 million is about 15G bytes. On the other hand, 
the memory usage of algorithm with deep-copy and size of 8 million is about 26G bytes.

@@

At the aggregating phase, each object is deep-copied or acquired with Arc once during the runtime in order to construct aggregated data structures.
If total number of objects is 1 million, the all of 1 million objects are deep-copied or cloned with Arc once during execution. 
Deep-copy allocates new memory for copied object. On the other hand, clone with Arc is merely acquisition of additional owner. 
Therefore, deep-copy is more expensive in terms of runtime and also use of memory than clone with Arc. 
Deep-copy processes all the original objects to generate newly deep-copied objects. 
This process has overhead and the existence of both original and copied objects doubles its memory usage.

After construction of aggregated data structure, the dropping variables of original objects occurs at the end of the aggregating phase.
In the algorithm with deep-copy, these variables are owners so that drop of variables triggers deallocation of actual values.
In the algorithm with Arc, the variables are Arc. The aggregated data structure contains Arc pointing to the same values pointed by original Arc.
Since the aggregated data structures continue to live after aggregating phase, drop of original Arcs does not triggers deallocation of values. 
Therefore, drop of original variables can shows overhead of memory deallocation in algorithm with deep-copy, 
and overhead of checking reference count of Arc in algorithm with Arc.

In addition, memory access from Arc is slower than ordinal variables due to the atomic operations. This may be potential overhead of the algorithm with Arc.

Considered these theoretical analysis and result of our experiment, using Arc improves runtime performance and memory usage compared to algorithms using deep-copy in tree-aggregate algorithms.

### 2020-06-28 thesis_template/4_Conclusion/conclusion.tex
corrected

Difference of variable types does not have impact on operation to access memory address where a value is located. 
This result gives us freedom of choices for variable types to construct complex objects in terms of runtime performance. 
When we however use borrowed types, such as references and slices, their lifetime should be explicitly defined. 
Therefore, we may use owner type variables to construct construct complex objects in order to facilitate lifetime tracking.

Runtime to drop Rc is much 60 times slower than normal reference. This is because Rc needs to check reference count to determine whether to deallocate its value. 
This result may say that we should use normal reference whenever it is possible. 
Again, tracking lifetime of references used in complex objects can be cumbersome. 
Choice of Rc and reference is dependent on complexity of object implemented.

In Rust, we can implement multithread programming with sharing data using Arc. In simple multithread algorithms, 
one can write code where shares data with Arc and simple reference among different threads.
Merge-sort algorithms sharing data with Arc is 21\% slower than normal reference. 
In this situation, sharing data with normal reference require relatively easy lifetime tracking, 
so we should use normal reference to share data among different thread whenever it is possible.

For more complex algorithms, like tree-aggregate and preprocess phase in KNN, one can implement algorithms sharing data with Arc or simply deep-copy the values.
The algorithms with deep-copy is about 40 to 50\% slower than the algorithm with Arc for complex objects.
When we however deal with String, the algorithms with deep-copy is faster than Arc. 
Therefore, the decision which to use deep-copy or Arc method should be determined based on complexity of objects.

@@

As we can see in the results of experiment, different memory strategy varies the performance of algorithms in Rust programming.
Which memory management strategy to take depends on what objects to deal with. 
Therefore, development of Big Data analysis tools in Rust programming should be started with objects implementation used in the systems.
Next, one can select suitable memory management strategies. 
Finally, algorithms can be optimized with more dedicated strategies to application setting, such as capacity of memory.

>>>>

Differences between variable types do not have an impact on operations to access memory address where a value is located. 
This result gives us freedom of choice for variable types to construct complex objects in terms of runtime performance. 
However when we use borrowed types, such as references and slices, their lifetime should be explicitly defined. 
Therefore, we may use owner type variables to construct complex objects in order to facilitate lifetime tracking.

Runtime to drop Rc is 60 times slower than normal reference. This is because Rc needs to check reference count to determine whether to deallocate its value. 
This result may say that we should use normal reference whenever it is possible. 
Again, tracking lifetime of references used in complex objects can be cumbersome. 
Choice of Rc and reference is dependent on complexity of objects implemented.

In Rust, we can implement multithread programming by sharing data using Arc. In simple multithread algorithms, 
one can write code that shares data with Arc and simple reference among different threads.
Merge-sort algorithms sharing data with Arc is 21\% slower than normal reference. 
In this situation, sharing data with normal reference require relatively easy lifetime tracking, 
so we should use normal reference to share data among different thread whenever it is possible.

For more complex algorithms, like tree-aggregate and preprocess phase in KNN, one can implement algorithms sharing data with Arc or simply deep-copy the values.
The algorithms with deep-copy are about 40 to 50\% slower than the algorithms with Arc for complex objects.
However when we deal with String, the algorithms with deep-copy are faster than Arc. 
Therefore, the decision on whether to use deep-copy or Arc method should be determined based on the complexity of objects.

@@

As we can see in the results of our experiments, different memory strategies vary the performance of algorithms in Rust programming.
Which memory management strategy to take depends on what objects to deal with. 
Therefore, development of Big Data analysis tools in Rust programming should be started with objects implementation used in the systems.
Next, one can select suitable memory management strategies. 
Finally, algorithms can be optimized with more dedicated strategies to application setting, such as capacity of memory.
